\ieeetitle

### 2017-02-08 report/main.tex
Change Miguel's University

	Dr Hugues Mercier, Institutes of Computer Science and Mathematics, University of Neuchâtel, Supervisor

	Dr Miguel Matos, HASLab - INESC TEC \&, University of Minho, Portugal,  Co-supervisor

>>>>

	Dr Hugues Mercier, Institutes of Computer Science and Mathematics, Université de Neuchâtel, Supervisor

	Dr Miguel Matos, INESC-ID/IST, Universidade de Lisboa, Portugal,  Co-supervisor
